EuPPollNet: A European database of plant-pollinator networks

### 2024-04-12 Manuscript/Ms.qmd
edits

```{r Load libraries, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE}
library(dplyr) #For handling fata 
library(sf) #For handling coordinates and plotting
library(scales) #For plotting (decimals on axes)
library(lubridate) #To operate with dates
library(tidyr) #Reshape data (wide format)
library(stringr) #Fix/modify strings
library(forcats)
library(readr)
#Load libraries for plotting
library(giscoR) #Maps
library(ggstar) #cool shapes as points
library(ggplot2) #general plotting
library(ggtree) #phylo trees
library(ggpattern) #cool shapes in barplots
library(patchwork) #plot organisation
library(cowplot) #plot organisation
library(viridis) #colours
library(ggnewscale)
library(ggtreeExtra)
library(kableExtra)

@@

#Average plant family coverage
d1 = readRDS("../Data/Manuscript_info/plant_coverage_phylo_RData")
mean_plant_fam_cov = d1 %>% 
ungroup() %>% 
filter(fam_group =="B") %>% 
summarise(mean_plant_fam_cov = mean(Percent)) %>% 
pull()

@@

The database contains a total of `r prettyNum(plant_spp_number, big.mark=",")` plant and `r prettyNum(pollinator_spp_number, big.mark=",")` pollinator species. The database coverage of flowering plants occurring in Europe is `r format(round(plant_coverage, 2), nsmall=2)`% (**Figure 4**), with an average coverage of `r format(round(mean_plant_fam_cov, 2), nsmall=2)`% at the plant family level. There are x% of families without recorded interactions and the absence of information seems to not follow strongly phylogenetic constraints (OUTPUT lambda)

>>>>

```{r Load libraries, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE}
library(dplyr) #For handling fata 
library(sf) #For handling coordinates and plotting
library(scales) #For plotting (decimals on axes)
library(lubridate) #To operate with dates
library(tidyr) #Reshape data (wide format)
library(stringr) #Fix/modify strings
library(forcats)
library(readr)
library(phytools)
#Load libraries for plotting
library(giscoR) #Maps
library(ggstar) #cool shapes as points
library(ggplot2) #general plotting
library(ggtree) #phylo trees
library(ggpattern) #cool shapes in barplots
library(patchwork) #plot organisation
library(cowplot) #plot organisation
library(viridis) #colours
library(ggnewscale)
library(ggtreeExtra)
library(kableExtra)

@@

#Average plant family coverage
d1 = readRDS("../Data/Manuscript_info/plant_coverage_phylo_RData") %>% 
filter(fam_group == "B")
#Average coverage per family
mean_plant_fam_cov = d1 %>% 
ungroup() %>% 
summarise(mean_plant_fam_cov = mean(Percent)) %>% 
pull()

#Percent of families with interaction records
all_fam = nrow(d1)
fam_with_data = d1 %>% 
filter(Percent > 0) %>% 
nrow()
percent_plant_fam_with_data = fam_with_data/all_fam * 100

#Calculate phylogenetic signal of presence-absence information
#Read data and plot it
tree = readRDS("../Data/Manuscript_info/plant_phylo.RData")
#Create binary trait to calculate phylo
phylo_trait = d1 %>% 
mutate(categorical = case_when(Percent > 0 ~ 1, TRUE ~ 0)) %>% 
#select(label, categorical) %>% 
ungroup() 
#Check phylogenetic signal
d1 = d1 %>% arrange(factor(label, levels = tree@phylo$tip.label))
phylo_signal_plant = phylosig(tree@phylo, phylo_trait$categorical, method="lambda", test=TRUE)
lambda_phylosig_plants = phylo_signal_plant$lambda
p_phylosig_plants = phylo_signal_plant$P

@@

The database contains a total of `r prettyNum(plant_spp_number, big.mark=",")` plant and `r prettyNum(pollinator_spp_number, big.mark=",")` pollinator species. The database coverage of flowering plants occurring in Europe is `r format(round(plant_coverage, 2), nsmall=2)`% (**Figure 4**), with an average coverage of `r format(round(mean_plant_fam_cov, 2), nsmall=2)`% at the plant family level. Most plant families have at least one species with interaction records (`r format(round(percent_plant_fam_with_data, 2), nsmall=2)`%) and the presence or absence of interaction data seems not to follow a phylogenetic pattern (RESULT).

`r lambda_phylosig_plants`
`r p_phylosig_plants`
